Appendix S2: Data Exploration

### 2022-01-22 ms/data_exploration.Rmd
Change dryad to figshare in SI2

All biodiversity metrics were calculated during the `targets` workflow (`_targets.R`), and are contained in the `biodiv_ferns_cent_dryad` object in the `targets` cache.

@@

```{r load-data, message = FALSE}
# Load the data from the targets workflow
tar_load(biodiv_ferns_cent_dryad)

# Alternatively, unzip `results.zip`
# (FIXME: add DOI when available)
# and read in the data from there
# biodiv_ferns_cent_dryad <- read_csv(here::here("japan_ferns_biodiv.csv"))
```

@@

```{r subset-vars}
biodiv_ferns_cent_raw <- 
  biodiv_ferns_cent_dryad %>%
  select(
    grids, lat, long, # grid-cell ID, latitude, longitude
    richness, pd_obs_z, fd_obs_z, rpd_obs_z, rfd_obs_z, # response vars
    percent_apo, temp, precip, precip_season, lat_area  # independent vars
  )
```

>>>>

All biodiversity metrics were calculated during the `targets` workflow (`_targets.R`), and are contained in the `biodiv_ferns_cent_figshare` object in the `targets` cache.

@@

```{r load-data, message = FALSE}
# Load the data from the targets workflow
tar_load(biodiv_ferns_cent_figshare)

# Alternatively, unzip `results.zip`
# (FIXME: add DOI when available)
# and read in the data from there
# biodiv_ferns_cent_figshare <- read_csv(here::here("japan_ferns_biodiv.csv"))
```

@@

```{r subset-vars}
biodiv_ferns_cent_raw <-
  biodiv_ferns_cent_figshare %>%
  select(
    grids, lat, long, # grid-cell ID, latitude, longitude
    richness, pd_obs_z, fd_obs_z, rpd_obs_z, rfd_obs_z, # response vars
    percent_apo, temp, precip, precip_season, lat_area  # independent vars
  )
```
